---
title: 'Race, Gender Disparities in Public Works'
author: "Jamison R. Crawford, MPA"
date: "January 24, 2019"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 4
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

<style>
body {
text-align: justify}
</style>

```{r packages, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}

options(scipen = 999)

if(!require(zoo)){install.packages("zoo")}
if(!require(tidyr)){install.packages("tidyr")}
if(!require(readr)){install.packages("readr")}
if(!require(dplyr)){install.packages("dplyr")}
if(!require(GGally)){install.packages("GGally")}
if(!require(scales)){install.packages("scales")}
if(!require(stringr)){install.packages("stringr")}
if(!require(ggplot2)){install.packages("ggplot2")}
if(!require(kableExtra)){install.packages("kableExtra")}

library(zoo)
library(tidyr)
library(readr)
library(dplyr)
library(GGally)
library(scales)
library(stringr)
library(ggplot2)
library(kableExtra)

rm(list = ls())

```

# Introduction

The following work analyzes four public construction projects in the Greater Syracuse area, including:

* [Empire Expo Center](https://en.wikipedia.org/wiki/Empire_Expo_Center)
* [Highway I-690](https://en.wikipedia.org/wiki/Interstate_690)
* [Lakeview Amphitheater](https://en.wikipedia.org/wiki/Lakeview_Amphitheater) 
* [Hancock International Airport](https://en.wikipedia.org/wiki/Syracuse_Hancock_International_Airport)

These records were procured by *Legal Services of Central New York* via the [Freedom of Information Act](https://en.wikipedia.org/wiki/Freedom_of_Information_Act_(United_States)).

All records are scraped, cleaned, and stored, including scripts and code books, in their respective Github repositories. The entire analysis, from raw data to the present publication, may be reproduced exactly with these resources - respectively, [Expo](https://github.com/jamisoncrawford/expo), [690](https://github.com/jamisoncrawford/690), [Lakeview](https://github.com/jamisoncrawford/lakeview), and [Hancock](https://github.com/jamisoncrawford/hancock). Analysis and publication scripts are stored in the [REIS](https://github.com/jamisoncrawford/reis) repository.

<br>

# Workforce Demographics

```{r loading, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}

names <- c("all_gross_race", "all_gross_sex",   "all_gross_sxrc", 
           "all_hours_race", "all_hours_sex",   "all_hours_sxrc", 
           "all_races",      "all_sexes",       "all_sxrc", 
           "expo_sex_class", "expo_race_class", "expo_rcsx_class")

files <- paste0(names, ".csv")
url <- "https://raw.githubusercontent.com/jamisoncrawford/reis/master/Datasets/"
urls <- paste0(url, files)

for (i in 1:length(names)){
  assign(names[i], read_csv(urls[i]))
}

rm(files, i, names, url, urls)

```

```{r all_sex, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}

tbl_all_sex <- all_sexes %>%
  select(sex:project) %>%
  rename("Gender" = sex, "Count" = count, "Percent" = percent, "Project" = project) %>%
  arrange(Project, desc(Gender), Percent)

viz_all_sex <- tbl_all_sex
tbl_all_sex <- tbl_all_sex %>%
  filter(Project != "Expo Center") %>%
  select(-Project) %>%
  mutate(Percent = percent(Percent, accuracy = 0.01))

```

<br>

## Demographic Overview

```{r sex, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}

sex <- all_sexes %>%
  as_data_frame() %>%
  filter(project != "Expo Center") %>%
  group_by(sex) %>%
  summarize(total = sum(count)) %>%
  as_data_frame() %>%
  mutate(percent = total / sum(total)) %>%
  rename("Gender" = sex, 
         "Total" = total, 
         "Percent" = percent)

tbl_sex <- sex %>%
  arrange(desc(Total)) %>%
  mutate(Percent = percent(Percent, accuracy = 0.01))

race <- all_races %>%
  as_data_frame() %>%
  filter(project != "Expo Center") %>%
  group_by(race) %>%
  summarize(total = sum(count)) %>%
  as_data_frame() %>%
  mutate(percent = total / sum(total)) %>%
  rename("Race" = race, "Total" = total, "Percent" = percent)

tbl_race <- race %>%
  arrange(desc(Total)) %>%
  mutate(Percent = percent(Percent, accuracy = 0.01))

sxrc <- all_sxrc %>%
  as_data_frame() %>%
  filter(project != "Expo Center") %>%
  group_by(sex, race) %>%
  summarize(total = sum(count)) %>%
  as_data_frame() %>%
  mutate(percent = total / sum(total)) %>%
  rename("Gender" = sex, "Race" = race, "Total" = total, "Percent" = percent)

tbl_sxrc <- sxrc %>%
  arrange(desc(Total)) %>%
  mutate(Percent = percent(Percent, accuracy = 0.01))
  
```

**Note****:** Due to the high aggregation of records on the "Exposition Center", it is impossible to determine unique workers. Therefore, "Expo Center" records are excluded from *Section 2: Workforce Demographics*. 

<br>

<center>

**Table 1: Workforce Gender Distribution**

```{r tbl_sex, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

kable(tbl_sex) %>%
  kable_styling(bootstrap_options = c("striped", 
                                      "hover", 
                                      "responsive"),
                font_size = 14,
                full_width = TRUE)

```

</center>

<br>

<center>

**Image 1: Workforce Gender Distribution**

```{r sex_dist_viz, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(sex, aes(x = Gender, y = Percent)) +
  coord_flip() +
  geom_bar(stat = "identity", fill = "skyblue") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::percent)

```

</center>

<center>

**Table 2: Workforce Race Distribution**

```{r tbl_race, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

kable(tbl_race) %>%
  kable_styling(bootstrap_options = c("striped", 
                                      "hover", 
                                      "responsive"),
                font_size = 14,
                full_width = TRUE)

```

</center>

<br>

<center>

**Image 2: Workforce Race Distribution**

```{r race_dist_viz, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(race, aes(x = reorder(Race, Total), y = Percent)) +
  coord_flip() +
  geom_bar(stat = "identity", fill = "skyblue") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::percent) +
  xlab("Race")

```

</center>

<br>

<center>

**Table 3: Workforce Gender & Race Distribution**

```{r tbl_sxrc, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

kable(tbl_sxrc) %>%
  kable_styling(bootstrap_options = c("striped", 
                                      "hover", 
                                      "responsive"),
                font_size = 14,
                full_width = TRUE)

```

</center>

<br>

<center>

**Image 3: Workforce Distribution by Gender & Race**

```{r sxrc_dist, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(sxrc, aes(x = reorder(Race, Total), y = Percent, fill = Gender)) +
  coord_flip() +
  geom_bar(stat = "identity") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::percent) +
  xlab("Race")

```

</center>

<br>

## Worker Gender by Project

<br>

<center>

**Table 4: Gender Distribution for All Projects**

```{r all_sex_tbl, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

kable(tbl_all_sex) %>%
  kable_styling(bootstrap_options = c("striped", 
                                      "hover", 
                                      "responsive"),
                font_size = 14,
                full_width = TRUE) %>%
  group_rows(group_label = "Hancock International", start_row = 1, end_row = 2) %>%
  group_rows(group_label = "Highway I-690", start_row = 3, end_row = 4) %>%
  group_rows(group_label = "Lakeview Amphitheater", start_row = 5, end_row = 6)

```

</center>

<br>

<center>

**Image 4: Gender Distribution for All Projects**

```{r all_sex_dist_viz, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

viz_all_sex <- viz_all_sex %>%
  filter(Project != "Expo Center") %>%
  arrange(Project, desc(Gender))

ggplot(viz_all_sex, aes(x = Project, y = Percent, fill = Gender)) +
  coord_flip() +
  geom_bar(stat = "identity") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::percent)

```

</center>

<br>

<center>

**Image 5: Gender Totals by Project**

```{r all_sex_count_viz, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(viz_all_sex, aes(x = Project, y = Count, fill = Gender)) +
  coord_flip() +
  geom_bar(stat = "identity", position = "dodge") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::number_format(big.mark = ","))

```

</center>

<br>

## Worker Race by Project

```{r all_race, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}

tbl_all_race <- all_races %>%
  select(race:project) %>%
  filter(project != "Expo Center") %>%
  rename("Race" = race, "Count" = count, "Percent" = percent, "Project" = project) %>%
  arrange(Project, desc(Percent))

viz_all_race <- tbl_all_race
tbl_all_race <- tbl_all_race %>% 
  select(-Project) %>%
  mutate(Percent = percent(Percent, accuracy = 0.01))

```

</center>

<br>

<center>

**Table 5: Race Distribution for All Projects**

```{r all_race_tbl, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

kable(tbl_all_race) %>%
  kable_styling(bootstrap_options = c("striped", 
                                      "hover", 
                                      "responsive"),
                font_size = 14,
                full_width = TRUE) %>%
  group_rows(group_label = "Hancock International", start_row = 1, end_row = 5) %>%
  group_rows(group_label = "Highway I-690", start_row = 6, end_row = 9) %>%
  group_rows(group_label = "Lakeview Amphitheater", start_row = 10, end_row = 14)

```

</center>

<br>

<center>

**Image 6: Race Distribution by Project**

```{r all_race_dist_viz, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(viz_all_race, aes(x = Project, y = Percent, fill = reorder(Race, Percent))) +
  coord_flip() +
  geom_bar(stat = "identity") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::percent) +
  theme(legend.title = element_text("Race")) +
  labs(fill = "Race")

```

</center>

<br>

<center>

**Image 7: Race Totals by Project**

```{r all_race_count_viz, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(viz_all_race, aes(x = reorder(Project, Count), y = Count, fill = reorder(Race, Count))) +
  coord_flip() +
  geom_bar(stat = "identity", position = "dodge") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::number_format(big.mark = ",")) +
  xlab("Project") +
  labs(fill = "Race")

```

</center>

<br>

## Race & Gender by Project

```{r all_sxrc, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}

tbl_all_sxrc <- all_sxrc %>%
  select(sex:project, -total) %>%
  filter(project != "Expo Center") %>%
  rename("Gender" = sex, "Race" = race, "Count" = count, "Percent" = percent, "Project" = project) %>%
  arrange(Project, desc(Percent))

viz_all_sxrc <- tbl_all_sxrc
tbl_all_sxrc <- tbl_all_sxrc %>% 
  select(-Project) %>%
  mutate(Percent = percent(Percent, accuracy = 0.01))

```

</center>

<br>

<center>

**Table 6: Race & Gender Distribution for All Projects**

```{r all_sxrc_tbl, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

kable(tbl_all_sxrc) %>%
  kable_styling(bootstrap_options = c("striped", 
                                      "hover", 
                                      "responsive"),
                font_size = 14,
                full_width = TRUE) %>%
  group_rows(group_label = "Hancock International", start_row = 1, end_row = 5) %>%
  group_rows(group_label = "Highway I-690", start_row = 6, end_row = 11) %>%
  group_rows(group_label = "Lakeview Amphitheater", start_row = 12, end_row = 19)

```

</center>

<br>

<center>

**Image 8: Race & Gender Distribution for All Projects**

```{r all_sxrc_dist_viz, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(viz_all_sxrc, aes(x = Gender, y = Percent, fill = Race)) +
  coord_flip() +
  geom_bar(stat = "identity") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::percent) +
  labs(fill = "Race") +
  facet_grid(Project ~ . )

```

</center>

<br>

<center>

**Image 9: Race & Gender Totals by Project**

```{r all_sxrc_count_viz, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(viz_all_sxrc, aes(x = Gender, y = Count, fill = Race)) +
  coord_flip() +
  geom_bar(stat = "identity", position = "dodge") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::number_format(big.mark = ",")) +
  xlab("Gender") +
  facet_grid(Project ~ . )

```

</center>

<br>

# Workforce Hourage

**Note****:** Though unique worker count is indeterminable per "Expo Center" records. However, the proportion of hours and gross pay by gender and race are available. Therefore, "Expo Center" records will now be included until otherwise stated.

```{r all_hours_sex, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

hrs_sx <- all_hours_sex %>%
  select(-total) %>%
  rename("Gender" = sex, "Count" = count, "Percent" = percent, "Project" = project)

hrs_rc <- all_hours_race %>%
  select(-total) %>%
  rename("Race" = race, "Count" = count, "Percent" = percent, "Project" = project)
  
hrs_sxrc <- all_hours_sxrc %>%
  select(-total) %>%
  rename("Gender" = sex, "Race" = race, "Count" = count, "Percent" = percent, "Project" = project)

hrs_sxrc[1:6, "Project"] <- "Hancock"

hrs_sx_wf <- hrs_sx %>%
  group_by(Gender) %>%
  summarize(Total = sum(Count)) %>%
  as_data_frame() %>%
  mutate(Percent = Total / sum(Total)) %>%
  arrange(desc(Percent))

hrs_rc_wf <- hrs_rc %>%
  group_by(Race) %>%
  summarize(Total = sum(Count)) %>%
  as_data_frame() %>%
  mutate(Percent = Total / sum(Total)) %>%
  arrange(desc(Percent))

hrs_sxrc_wf <- hrs_sxrc %>%
  group_by(Gender, Race) %>%
  summarize(Total = sum(Count)) %>%
  as_data_frame() %>%
  mutate(Percent = Total / sum(Total)) %>%
  filter(!is.na(Race),
         Total > 0.0) %>%
  arrange(desc(Percent))

```

<br>

## Hourage Overview 

<center>

**Table 7: Hourage Distribution by Gender, All Projects**

```{r hrs_sx_wf_tbl, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

hrs_sx_wf_tbl <- hrs_sx_wf %>%
  mutate(Percent = percent(Percent, accuracy = 0.01),
         Total = number(Total, big.mark = ","))

kable(hrs_sx_wf_tbl) %>%
  kable_styling(bootstrap_options = c("striped", 
                                      "hover", 
                                      "responsive"),
                font_size = 14,
                full_width = TRUE)

```

</center>

<br>

<center>

**Image 10: Workforce Hourage Distribution by Gender**

```{r hrs_sx_wf_viz, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(hrs_sx_wf, aes(x = Gender, y = Percent)) +
  coord_flip() +
  geom_bar(stat = "identity", fill = "skyblue") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::percent)

```

</center>

<br>

<center>

**Table 8: Workforce Hourage Distribution by Race, All Projects**

```{r hrs_rc_wf_tbl, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

hrs_rc_wf_tbl <- hrs_rc_wf %>%
  mutate(Percent = percent(Percent, accuracy = 0.01),
         Total = number(Total, big.mark = ",", accuracy = 2))

kable(hrs_rc_wf_tbl) %>%
  kable_styling(bootstrap_options = c("striped", 
                                      "hover", 
                                      "responsive"),
                font_size = 14,
                full_width = TRUE)

```

</center>

<br>

<center>

**Image 11: Workforce Hourage Distribution by Race**

```{r hrs_rc_wf_viz, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(hrs_rc_wf, aes(x = reorder(Race, Total), y = Percent)) +
  coord_flip() +
  geom_bar(stat = "identity", fill = "skyblue") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::percent) +
  xlab("Race")

```

</center>

<br>

<center>

**Table 9: Workforce Hourage Distribution by Gender & Race, All Projects**

```{r hrs_sxrc_wf_tbl, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

hrs_sxrc_wf_tbl <- hrs_sxrc_wf %>%
  mutate(Percent = percent(Percent, accuracy = 0.01),
         Total = number(Total, big.mark = ",", accuracy = 2))

kable(hrs_sxrc_wf_tbl) %>%
  kable_styling(bootstrap_options = c("striped", 
                                      "hover", 
                                      "responsive"),
                font_size = 14,
                full_width = TRUE)

```

</center>

<br>

<center>

**Image 12: Workforce Hourage Distribution by Gender & Race**

```{r sxrc_hrs_dist_viz, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(hrs_sxrc_wf, aes(x = reorder(Race, Total), y = Percent, fill = Gender)) +
  coord_flip() +
  geom_bar(stat = "identity") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::percent) +
  xlab("Race")

```

</center>

<br>

## Hourage by Gender & Project

```{r sex_hourage_setup, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

hrs_rc <- all_hours_race %>%
  select(-total) %>%
  rename("Race" = race, "Count" = count, "Percent" = percent, "Project" = project)

hrs_sx <- hrs_sx %>% arrange(Project, desc(Count), Gender)
hrs_rc <- hrs_rc %>% arrange(Project, desc(Count), Race)
hrs_sxrc <- hrs_sxrc %>% arrange(Project, desc(Count), Gender, Race)

hrs_sx_viz <- hrs_sx
hrs_rc_viz <- hrs_rc
hrs_sxrc_viz <- hrs_sxrc

hrs_sx_tbl <- hrs_sx %>%
  mutate(Count = number(Count, big.mark = ",", accuracy = 2),
         Percent = percent(Percent, accuracy = 0.01))

hrs_rc <- hrs_rc %>%
  select(-Percent) %>%
  ungroup() %>%
  group_by(Project, Race) %>%
  summarize(Count = sum(Count)) %>%
  ungroup() %>%
  arrange(Project, desc(Count))

totals <- hrs_rc %>%
  group_by(Project) %>%
  summarize(Total = sum(Count))
  
totals <- totals$Total

n_tots <- c(rep(x = totals[1], times = 5),
            rep(x = totals[2], times = 5),
            rep(x = totals[3], times = 4),
            rep(x = totals[4], times = 5))

hrs_rc$Total <- n_tots

hrs_rc <- hrs_rc %>%
  ungroup() %>%
  mutate(Percent = Count / Total) %>%
  select(-Total)

hrs_rc_viz <- hrs_rc

hrs_rc_tbl <- hrs_rc %>%
  mutate(Count = number(Count, big.mark = ","),
         Percent = percent(Percent, accuracy = 0.01))

hrs_sxrc_tbl <- hrs_sxrc %>%
  mutate(Count = number(Count, big.mark = ",", accuracy = 2),
         Percent = percent(Percent, accuracy = 0.01)) %>%
  filter(!is.na(Gender))

```

</center>

<br>

<center>

**Table 10: Workforce Hourage Distribution by Gender & Project**

```{r hrs_by_sex_project, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

hrs_sx_tbl <- hrs_sx_tbl %>% select(-Project)

kable(hrs_sx_tbl) %>%
  kable_styling(bootstrap_options = c("striped", 
                                      "hover", 
                                      "responsive"),
                font_size = 14,
                full_width = TRUE) %>%
  group_rows(group_label = "Exposition Center", start_row = 1, end_row = 2) %>%
  group_rows(group_label = "Hancock International", start_row = 3, end_row = 4) %>%
  group_rows(group_label = "Highway I-690", start_row = 5, end_row = 6) %>%
  group_rows(group_label = "Lakeview Amphitheater", start_row = 7, end_row = 8)

```

</center>

<br>

<center>

**Image 13: Hourage Distribution by Gender & Projects**

```{r hrs_sx_viz_dist, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(hrs_sx_viz, aes(x = Project, y = Percent, fill = reorder(Gender, Percent))) +
  coord_flip() +
  geom_bar(stat = "identity") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::percent) +
  theme(legend.title = element_text("Gender")) +
  labs(fill = "Gender")

```

</center>

<br>

<center>

**Image 14: Hourage Totals by Gender & Project**

```{r hrs_sx_viz_count, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(hrs_sx_viz, aes(x = reorder(Project, Count), y = Count, fill = Gender)) +
  coord_flip() +
  geom_bar(stat = "identity", position = "dodge") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::number_format(big.mark = ",")) +
  xlab("Project")

```

</center>

<br>

## Hourage by Race & Project

<br>

<center>

**Table 11: Workforce Hourage Distribution by Sex & Project**

```{r hrs_by_rc_project, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

hrs_rc_tbl <- hrs_rc_tbl %>% select(-Project)

kable(hrs_rc_tbl) %>%
  kable_styling(bootstrap_options = c("striped", 
                                      "hover", 
                                      "responsive"),
                font_size = 14,
                full_width = TRUE) %>%
  group_rows(group_label = "Exposition Center", start_row = 1, end_row = 5) %>%
  group_rows(group_label = "Hancock International", start_row = 6, end_row = 10) %>%
  group_rows(group_label = "Highway I-690", start_row = 11, end_row = 14) %>%
  group_rows(group_label = "Lakeview Amphitheater", start_row = 15, end_row = 19)

```

</center>

<br>

<center>

**Image 14: Race Distribution for All Projects**

```{r hrs_rc_viz_dist, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(hrs_rc_viz, aes(x = Project, y = Percent, fill = reorder(Race, Percent))) +
  coord_flip() +
  geom_bar(stat = "identity") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::percent) +
  theme(legend.title = element_text("Gender")) +
  labs(fill = "Race") +
  xlab("Hours (%)")

```

</center>

<br>

<center>

**Image 15: Race Totals by Project**

```{r hrs_rc_viz_count, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(hrs_rc_viz, aes(x = reorder(Project, Count), y = Count, fill = Race)) +
  coord_flip() +
  geom_bar(stat = "identity", position = "dodge") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::number_format(big.mark = ",")) +
  xlab("Project") +
  ylab("Total Hours")

```

</center>

<br>

## Hourage by Gender, Race, Project

```{r hrs_sxrc_project, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

hrs_sxrc <- all_hours_sxrc %>%
  rename("Gender" = sex, "Race" = race, 
         "Count" = count, "Total" = total, 
         "Percent" = percent, "Project" = project) %>%
  select(-Total) %>%
  arrange(Project, desc(Count)) %>%
  filter(!is.na(Race),
         Count != 0) %>%
  as_data_frame()

hrs_sxrc_viz <- hrs_sxrc

hrs_sxrc_tbl <- hrs_sxrc %>% 
  mutate(Count = number(Count, big.mark = ",", accuracy = 2),
         Percent = percent(Percent, accuracy = 0.01)) %>%
  as_data_frame()

hrs_sxrc_tbl <- as.data.frame(hrs_sxrc_tbl)

file <- "~/Projects/REIS/Master/hrs_sxrc.rds"

save(hrs_sxrc_tbl, file = file)

load(file)

```

<br>

<center>

**Table 12: Workforce Hourage Distribution by Sex, Race, & Project**

```{r hrs_sxrc_proj_tbl, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

load(file)

hrs_sxrc_tbl <- hrs_sxrc_tbl %>% select(-Project)

kable(hrs_sxrc_tbl) %>%
  kable_styling(bootstrap_options = c("striped"),
                font_size = 14,
                full_width = TRUE) %>%
  group_rows(group_label = "Exposition Center", start_row = 1, end_row = 8) %>%
  group_rows(group_label = "Hancock International", start_row = 9, end_row = 13) %>%
  group_rows(group_label = "Highway I-690", start_row = 14, end_row = 19) %>%
  group_rows(group_label = "Lakeview Amphitheater", start_row = 20, end_row = 27)

```

</center>

<br>

<center>

**Image 16: Workforce Hourage Distribution by Sex, Race, & Project**

```{r hrs_sxrc_viz_dist, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(hrs_sxrc_viz, aes(x = reorder(Gender, Count), y = Percent, fill = reorder(Race, Percent))) +
  coord_flip() +
  geom_bar(stat = "identity") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::percent) +
  theme(legend.title = element_text("Gender")) +
  labs(fill = "Race") +
  xlab("") +
  ylab("Hours (%)") +
  facet_grid(Project ~ .)

```

</center>

<br>

<center>

**Image 17: Workforce Hourage Count by Sex, Race, & Project**

```{r hrs_sxrc_viz_count, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(hrs_sxrc_viz, aes(x = reorder(Gender, Count), y = Count, fill = Race)) +
  coord_flip() +
  geom_bar(stat = "identity", position = "dodge") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::number_format(big.mark = ",")) +
  xlab("") +
  ylab("Total Hours") +
  facet_grid(Project ~ .)

```

</center>

<br>

# Workforce Gross Wages 

```{r grs_sx_wf_tbl, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

gross_sex <- all_gross_sex %>%
  group_by(sex) %>%
  summarize(count = sum(count)) %>%
  as_data_frame() %>%
  arrange(desc(count)) %>%
  rename("Gender" = sex, "Count" = count) %>%
  mutate(Total = sum(Count),
         Percent = Count / Total)

gross_sex_viz <- gross_sex

gross_sex_tbl <- gross_sex %>%
  mutate(Percent = percent(Percent, accuracy = 0.01),
         Count = dollar(Count, big.mark = ",", accuracy = 2)) %>%
  select(-Total)

```

<br>

## Gross Wages Overview

<br>

<center>

**Table 13: Gross Wage Distribution by Gender**

```{r grs_sx_wf_tbl2, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

kable(gross_sex_tbl) %>%
  kable_styling(bootstrap_options = c("striped", 
                                      "hover", 
                                      "responsive"),
                font_size = 14,
                full_width = TRUE)

```

</center>

<br>

<center>

**Image 18: Gross Wage Distribution by Gender**

```{r gross_sex_viz, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(gross_sex_viz, aes(x = Gender, y = Percent)) +
  coord_flip() +
  geom_bar(stat = "identity", fill = "skyblue") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::percent)

```

</center>

<br>

<center>

**Table 14: Gross Wage Distribution by Race**

```{r grs_rc_wf_tbl, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

gross_race <- all_gross_race %>%
  group_by(race) %>%
  summarize(count = sum(count)) %>%
  as_data_frame() %>%
  arrange(desc(count)) %>%
  rename("Race" = race, "Count" = count) %>%
  mutate(Total = sum(Count),
         Percent = Count / Total)

gross_race_viz <- gross_race

gross_race_tbl <- gross_race %>%
  mutate(Percent = percent(Percent, accuracy = 0.01),
         Count = dollar(Count, big.mark = ",", accuracy = 2)) %>%
  select(-Total)

kable(gross_race_tbl) %>%
  kable_styling(bootstrap_options = c("striped", 
                                      "hover", 
                                      "responsive"),
                font_size = 14,
                full_width = TRUE)

```

</center>

<br>

<center>

**Image 19: Gross Wage Distribution by Race**

```{r grs_rc_wf_viz, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(gross_race_viz, aes(x = reorder(Race, Count), y = Percent)) +
  coord_flip() +
  geom_bar(stat = "identity", fill = "skyblue") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::percent) +
  xlab("") +
  ylab("Total Gross (%)")

```

</center>

<br>

<center>

**Table 15: Gross Wage by Gender & Race**

```{r grs_sxrc_wf_tbl, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

gross_sxrc <- all_gross_sxrc %>%
  group_by(sex, race) %>%
  summarize(count = sum(count)) %>%
  as_data_frame() %>%
  rename("Gender" = sex, "Race" = race, "Count" = count) %>%
  mutate(Total = sum(Count),
         Percent = Count / Total) %>%
  arrange(desc(Percent))

gross_sxrc_viz <- gross_sxrc

gross_sxrc_tbl <- gross_sxrc %>%
  mutate(Percent = percent(Percent, accuracy = 0.01),
         Count = dollar(Count, big.mark = ",", accuracy = 2)) %>%
  select(-Total)

kable(gross_sxrc_tbl) %>%
  kable_styling(bootstrap_options = c("striped", 
                                      "hover", 
                                      "responsive"),
                font_size = 14,
                full_width = TRUE)

```

</center>

<br>

<center>

**Image 20: Gross Wage Distribution by Gender & Race**

```{r sxrc_grs_dist_viz, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(gross_sxrc_viz, aes(x = reorder(Race, Percent), y = Percent, fill = Gender)) +
  coord_flip() +
  geom_bar(stat = "identity") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::percent) +
  xlab("Race")

```

</center>

<br>

## Gross by Gender & Project

```{r sxrc_gross_all_setup, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

gp_sex <- all_gross_sex %>% 
  rename("Gender" = sex, "Count" = count, "Total" = total, "Percent" = percent, "Project" = project) %>%
  select(-Total) %>%
  arrange(Project, desc(Percent))

gp_sex_viz <- gp_sex
gp_sex_tbl <- gp_sex %>%
  mutate(Percent = percent(Percent, accuracy = 0.01),
         Count = dollar(Count, big.mark = ",", accuracy = 2))
  

gp_race <- all_gross_race %>% 
  rename("Race" = race, "Count" = count, "Total" = total, "Percent" = percent, "Project" = project) %>%
  select(-Total) %>%
  arrange(Project, desc(Percent))

gp_race_viz <- gp_race
gp_race_tbl <- gp_race %>%
  mutate(Percent = percent(Percent, accuracy = 0.01),
         Count = dollar(Count, big.mark = ",", accuracy = 2))


gp_sxrc_all <- all_gross_sxrc %>% 
  rename("Gender" = sex, "Race" = race, "Count" = count, "Total" = total, "Percent" = percent, "Project" = project) %>%
  select(-Total) %>%
  arrange(Project, desc(Percent))

gp_sxrc_viz <- gp_sxrc_all
gp_sxrc_tbl <- gp_sxrc_all %>%
  mutate(Percent = percent(Percent, accuracy = 0.01),
         Count = dollar(Count, big.mark = ",", accuracy = 2))

```

</center>

<br>

<center>

**Table 16: Gross Wage Distribution by Gender & Project**

```{r grs_by_sex_project, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

gp_sex_tbl <- gp_sex_tbl %>% select(-Project)

kable(gp_sex_tbl) %>%
  kable_styling(bootstrap_options = c("striped", 
                                      "hover", 
                                      "responsive"),
                font_size = 14,
                full_width = TRUE) %>%
  group_rows(group_label = "Exposition Center", start_row = 1, end_row = 2) %>%
  group_rows(group_label = "Hancock International", start_row = 3, end_row = 3) %>%
  group_rows(group_label = "Highway I-690", start_row = 4, end_row = 5) %>%
  group_rows(group_label = "Lakeview Amphitheater", start_row = 6, end_row = 7)

```

</center>

<br>

<center>

**Image 21: Gross Wage Distribution by Gender & Projects**

```{r grs_sx_viz_dist, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(gp_sex_viz, aes(x = Project, y = Percent, fill = reorder(Gender, Percent))) +
  coord_flip() +
  geom_bar(stat = "identity") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::percent) +
  theme(legend.title = element_text("Gender")) +
  labs(fill = "Gender")

```

</center>

<br>

<center>

**Image 22: Gross Wage Totals by Gender & Project**

```{r grs_sx_viz_count, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(gp_sex_viz, aes(x = reorder(Project, Count), y = Count, fill = Gender)) +
  coord_flip() +
  geom_bar(stat = "identity", position = "dodge") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::number_format(big.mark = ",", prefix = "$")) +
  ylab("Gross Wages") +
  xlab("")

```

</center>

<br>

## Wages by Race & Project

<br>

<center>

**Table 17: Gross Wage Distribution by Sex & Project**

```{r grs_by_rc_project, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

gp_race_tbl <- gp_race_tbl %>% select(-Project)

kable(gp_race_tbl) %>%
  kable_styling(bootstrap_options = c("striped", 
                                      "hover", 
                                      "responsive"),
                font_size = 14,
                full_width = TRUE) %>%
  group_rows(group_label = "Exposition Center", start_row = 1, end_row = 5) %>%
  group_rows(group_label = "Hancock International", start_row = 6, end_row = 10) %>%
  group_rows(group_label = "Highway I-690", start_row = 11, end_row = 14) %>%
  group_rows(group_label = "Lakeview Amphitheater", start_row = 15, end_row = 19)

```

</center>

<br>

<center>

**Image 23: Gross Wage Distribution for All Projects**

```{r grs_rc_viz_dist, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(gp_race_viz, aes(x = Project, y = Percent, fill = reorder(Race, Percent))) +
  coord_flip() +
  geom_bar(stat = "identity") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::percent) +
  theme(legend.title = element_text("Gender")) +
  labs(fill = "Race") +
  xlab("")

```

</center>

<br>

<center>

**Image 24: Gross Wage Totals by Race & Project**

```{r grs_rc_viz_count, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(gp_race_viz, aes(x = reorder(Project, Count), y = Count, fill = Race)) +
  coord_flip() +
  geom_bar(stat = "identity", position = "dodge") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::number_format(big.mark = ",", prefix = "$")) +
  xlab("") +
  ylab("Total Gross")

```

</center>

<br>

## Gross by Gender, Race, Project

```{r grs_sxrc_proj_tbl_2, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

url <- "https://raw.githubusercontent.com/jamisoncrawford/reis/master/Datasets/all_gross_sxrc.csv"
gp_sxrc <- read_csv(url)

gp_sxrc <- gp_sxrc %>% 
  rename("Gender" = sex,
         "Race" = race,
         "Count" = count,
         "Total" = total,
         "Percent" = percent,
         "Project" = project) %>%
  select(-Total) %>%
  as_tibble() %>%
  arrange(Project, desc(Count))

gp_sxrc_viz <- gp_sxrc

gp_sxrc_tbl <- gp_sxrc %>%
  mutate(Count = number(Count, big.mark = ",", accuracy = 2),
         Percent = percent(Percent, accuracy = 0.01))
  
```

<br>

<center>

**Table 18: Gross Wage Distribution by Sex, Race, & Project**

```{r grs_sxrc_proj_tbl_3, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

gp_sxrc_tbl <- gp_sxrc_tbl %>% select(-Project)

kable(gp_sxrc_tbl) %>%
  kable_styling(bootstrap_options = c("striped"),
                font_size = 14,
                full_width = TRUE) %>%
  group_rows(group_label = "Exposition Center", start_row = 1, end_row = 8) %>%
  group_rows(group_label = "Hancock International", start_row = 9, end_row = 13) %>%
  group_rows(group_label = "Highway I-690", start_row = 14, end_row = 19) %>%
  group_rows(group_label = "Lakeview Amphitheater", start_row = 20, end_row = 27)

```

</center>

<br>

<center>

**Image 25: Gross Wage Distribution by Sex, Race, & Project**

```{r grs_sxrc_viz_dist, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(gp_sxrc_viz, aes(x = reorder(Gender, Count), y = Percent, fill = reorder(Race, Percent))) +
  coord_flip() +
  geom_bar(stat = "identity") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::percent) +
  theme(legend.title = element_text("Gender")) +
  labs(fill = "Race") +
  xlab("") +
  ylab("Gross Pay (%)") +
  facet_grid(Project ~ .)

```

</center>

<br>

<center>

**Image 26: Gross Wage Total by Sex, Race, & Project**

```{r grs_sxrc_viz_count, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=7, cache=TRUE}

ggplot(gp_sxrc_viz, aes(x = reorder(Gender, Count), y = Count, fill = Race)) +
  coord_flip() +
  geom_bar(stat = "identity", position = "dodge") +
  theme_classic() +
  theme(text = element_text(size = 18), 
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14)) +
  scale_y_continuous(labels = scales::number_format(big.mark = ",", prefix = "$")) +
  xlab("") +
  ylab("Total Gross") +
  facet_grid(Project ~ .)

```

</center>

<br>

# Lakeview & Hancock

<br>

## Records Overview

<br>

```{r message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}

url <- "https://raw.githubusercontent.com/jamisoncrawford/reis/master/Datasets/lakeview_hancock_merge.csv"
lvhc <- read_csv(url); rm(url)

lvhc[which(lvhc$sex == "male"), "sex"] <- "Male"

lvhc_recs_uniq <- lvhc %>%
  filter(!is.na(project),
         !is.na(ssn)) %>%
  select(project:name, ssn, sex:race) %>%
  unique() %>%
  group_by(project) %>%
  summarize(unique = n(),
            race_recs = sum(!is.na(race)),
            race_perc = race_recs / unique,
            sex_recs = sum(!is.na(sex)),
            sex_perc = sex_recs / unique) %>%    # Note: Uniqueness determined by project, ssn, ignores zip
  ungroup() %>% 
  mutate(unique = number(unique, big.mark = ","),
         race_recs = number(race_recs, big.mark = ","),
         race_perc = percent(race_perc, accuracy = 0.01),
         sex_recs = number(sex_recs, big.mark = ","),
         sex_perc = percent(sex_perc, accuracy = 0.01)) %>%
  rename("Project" = project,
         "Total Workers" = unique,
         "Race Disclosed" = race_recs,
         "Race Disclosed (%)" = race_perc,
         "Gender Disclosed" = sex_recs,
         "Gender Disclosed (%)" = sex_perc)
  
  
lvhc_recs <- lvhc %>%
  filter(!is.na(project),
         !is.na(ssn)) %>%
  group_by(project) %>%
  summarize(unique = n(),
            race_recs = sum(!is.na(race)),
            race_perc = race_recs / unique,
            sex_recs = sum(!is.na(sex)),
            sex_perc = sex_recs / unique,
            zip_recs = sum(!is.na(zip)),
            zip_perc = sex_recs / unique,
            grs_recs = sum(!is.na(gross)),
            grs_perc = grs_recs / unique) %>%     # Note: Revealed Records Breakdown
  ungroup() %>% 
  mutate(unique = number(unique, big.mark = ","),
         race_recs = number(race_recs, big.mark = ","),
         race_perc = percent(race_perc, accuracy = 0.01),
         sex_recs = number(sex_recs, big.mark = ","),
         sex_perc = percent(sex_perc, accuracy = 0.01),
         zip_recs = number(zip_recs, big.mark = ","),
         zip_perc = percent(zip_perc, accuracy = 0.01),
         grs_recs = number(grs_recs, big.mark = ","),
         grs_perc = percent(grs_perc, accuracy = 0.01)) %>%
  rename("Project" = project,
         "Total Workers" = unique,
         "Race Disclosed" = race_recs,
         "Race Disclosed (%)" = race_perc,
         "Gender Disclosed" = sex_recs,
         "Gender Disclosed (%)" = sex_perc,
         "ZIP Disclosed" = zip_recs,
         "ZIP Disclosed (%)" = zip_perc,
         "Gross Disclosed" = grs_recs,
         "Gross Disclosed (%)" = grs_perc)
  
lvhc_rec_cons <- lvhc %>%
  filter(!is.na(project)) %>%
  group_by(project, name) %>%
  summarize(`Unique Records` = n()) %>%
  ungroup()

tmp_tots <- lvhc_rec_cons %>%
  group_by(project) %>%
  summarize(Total = sum(`Unique Records`)) %>%
  ungroup()

lvhc_rec_cons <- left_join(lvhc_rec_cons, 
                           tmp_tots, 
                           by = "project") %>%
  rename("Project" = project,
         "Contractor" = name) %>%
  mutate(Percent = `Unique Records` / Total) %>%
  arrange(Project, desc(Percent)) %>%
  mutate(`Unique Records` = number(`Unique Records`, big.mark = ","),
         Total = number (Total, big.mark = ","),
         Percent = percent(Percent, accuracy = 0.01)) %>%
  rename(`Project Total` = Total)

# Race & Gender by Contractor

con_race <- lvhc %>%
  filter(!is.na(project),
         !is.na(ssn)) %>%
  select(project:name, ssn, sex:race) %>%
  unique() %>%
  group_by(project, name, race) %>%
  summarize(total = n()) %>%
  ungroup() %>%
  arrange(project, reorder(name, desc(total)), reorder(race, desc(total)))

proj_tots <- lvhc %>%
  filter(!is.na(project),
         !is.na(ssn)) %>%
  select(project:name, ssn, sex:race) %>%
  unique() %>%
  group_by(project) %>%
  summarize(proj_total = sum(n())) %>%
  ungroup()

name_tots <- lvhc %>%
  filter(!is.na(project),
         !is.na(ssn)) %>%
  select(project:name, ssn, sex:race) %>%
  unique() %>%
  group_by(project, name) %>%
  summarize(name_total = sum(n())) %>%
  ungroup()

con_race_viz <- con_race %>%
  left_join(name_tots, by = c("project", "name")) %>%
  left_join(proj_tots, by = "project") %>%
  mutate(name_perc = total / name_total,
         proj_perc = total / proj_total) %>%
  select(project:name_total, name_perc, proj_total, proj_perc)

con_race_tbl <- con_race_viz %>%
  mutate(name_perc = percent(name_perc, accuracy = 0.01),
         proj_perc = percent(proj_perc, accuracy = 0.01)) %>%
  rename("Project" = project,
         "Company" = name,
         "Race" = race,
         "Workers of Race" = total,
         "Total Company Workers" = name_total,
         "Company Workers (%)" = name_perc,
         "Total Project Workers" = proj_total,
         "Project Workers (%)" = proj_perc)                        # Workers by Company & Race

con_sex <- lvhc %>%
  filter(!is.na(project),
         !is.na(ssn)) %>%
  select(project:name, ssn, sex:race) %>%
  unique() %>%
  group_by(project, name, sex) %>%
  summarize(total = n()) %>%
  ungroup() %>%
  arrange(project, reorder(name, desc(total)), reorder(sex, desc(total)))

con_sex_viz <- con_sex %>%
  left_join(name_tots, by = c("project", "name")) %>%
  left_join(proj_tots, by = "project") %>%
  mutate(name_perc = total / name_total,
         proj_perc = total / proj_total) %>%
  select(project:name_total, name_perc, proj_total, proj_perc)

con_sex_tbl <- con_sex_viz %>%
  mutate(name_perc = percent(name_perc, accuracy = 0.01),
         proj_perc = percent(proj_perc, accuracy = 0.01)) %>%
  rename("Project" = project,
         "Company" = name,
         "Gender" = sex,
         "Workers of Gender" = total,
         "Total Company Workers" = name_total,
         "Company Workers (%)" = name_perc,
         "Total Project Workers" = proj_total,
         "Project Workers (%)" = proj_perc)                        # Workers by Company & Sex

con_sxrc <- lvhc %>%
  filter(!is.na(project),
         !is.na(ssn)) %>%
  select(project:name, ssn, sex:race) %>%
  unique() %>%
  group_by(project, name, sex, race) %>%
  summarize(total = n()) %>%
  ungroup() %>%
  arrange(project, reorder(name, desc(total)), reorder(sex, desc(total)), reorder(race, desc(total)))

con_sxrc_viz <- con_sxrc %>%
  left_join(name_tots, by = c("project", "name")) %>%
  left_join(proj_tots, by = "project") %>%
  mutate(name_perc = total / name_total,
         proj_perc = total / proj_total) %>%
  select(project:name_total, name_perc, proj_total, proj_perc)

con_sxrc_tbl <- con_sxrc_viz %>%
  mutate(name_perc = percent(name_perc, accuracy = 0.01),
         proj_perc = percent(proj_perc, accuracy = 0.01)) %>%
  rename("Project" = project,
         "Company" = name,
         "Gender" = sex,
         "Race" = race,
         "Workers of Gender & Race" = total,
         "Total Company Workers" = name_total,
         "Company Workers (%)" = name_perc,
         "Total Project Workers" = proj_total,
         "Project Workers (%)" = proj_perc)                        # Workers by Company & Sex/Race

```

<br>

### Unique Workers

<br>

```{r echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE}

library(kableExtra)

kable(lvhc_recs_uniq) %>%
  kable_styling(bootstrap_options = c("striped"),
                font_size = 14,
                full_width = TRUE)

```

<br>

### Unique Records

<br>

```{r echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE}

library(dplyr)

lvhc_recs_tbl <- lvhc_recs %>%
  rename(`Total Records` = `Total Workers`)

kable(lvhc_recs_tbl) %>%
  kable_styling(bootstrap_options = c("striped"),
                font_size = 14,
                full_width = TRUE)

```

<br>

### Unique Records by Contractor

<br>

```{r echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE}

library(kableExtra)

lvhc_rec_cons_tbl <- lvhc_rec_cons %>%
  select(-Project)

kable(lvhc_rec_cons) %>%
  kable_styling(bootstrap_options = c("striped"),
                font_size = 14,
                full_width = TRUE) %>%
  group_rows(group_label = "Hancock International", start_row = 1, end_row = 9) %>%
  group_rows(group_label = "Lakeview Amphitheater", start_row = 10, end_row = 36)

```

<br>

## Workers by Contractor

<br>

### Workers by Race & Contractor

<br>

```{r echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE}

con_race_tbl2 <- con_race_tbl %>%
  select(-Project)

kable(con_race_tbl2) %>%
  kable_styling(bootstrap_options = c("striped"),
                font_size = 14,
                full_width = TRUE) %>%
  group_rows(group_label = "Hancock International", start_row = 1, end_row = 15) %>%
  group_rows(group_label = "Lakeview Amphitheater", start_row = 16, end_row = 67)

```

<br>

### Workers by Gender & Contractor

<br>

```{r echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE}
con_sex_tbl <- con_sex_tbl %>%
  select(-Project)

kable(con_sex_tbl) %>%
  kable_styling(bootstrap_options = c("striped"),
                font_size = 14,
                full_width = TRUE) %>%
  group_rows(group_label = "Hancock International", start_row = 1, end_row = 8) %>%
  group_rows(group_label = "Lakeview Amphitheater", start_row = 9, end_row = 46)

```

<br>

### Race & Gender by Contractor

<br>

```{r echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE}

con_sxrc_tbl2 <- con_sxrc_tbl %>%
  select(-Project)

kable(con_sxrc_tbl2) %>%
  kable_styling(bootstrap_options = c("striped"),
                font_size = 14,
                full_width = TRUE) %>%
  group_rows(group_label = "Hancock International", start_row = 1, end_row = 15) %>%
  group_rows(group_label = "Lakeview Amphitheater", start_row = 16, end_row = 79)

```

<br>

## Wages & Hours

```{r echo = FALSE, message = FALSE, warning = FALSE, cache = TRUE}
# Pay & Hours by Gender & Race

tot_hours <- lvhc %>%
  filter(!is.na(ssn),
         !is.na(project),
         !is.na(hours)) %>%
  select(project, name, ssn, sex, race, hours) %>%
  group_by(project, name, ssn, sex, race) %>%
  summarize(total = sum(hours)) %>%
  ungroup()

proj_tots <- lvhc %>%
  filter(!is.na(project),
         !is.na(ssn),
         !is.na(hours)) %>%
  select(project:name, ssn, sex:race, hours) %>%
  group_by(project) %>%
  summarize(proj_total = sum(hours, na.rm = TRUE)) %>%
  ungroup()

name_tots <- lvhc %>%
  filter(!is.na(project),
         !is.na(ssn),
         !is.na(hours)) %>%
  select(project:name, ssn, sex:race, hours) %>%
  group_by(project, name) %>%
  summarize(name_total = sum(n())) %>%
  ungroup()

tot_hrs_sx_viz <- tot_hours %>%
  group_by(project, sex) %>%
  summarize(tot_hrs = sum(total)) %>%
  arrange(project, desc(`tot_hrs`)) %>%
  ungroup() %>%
  left_join(proj_tots, by = "project") %>%
  mutate(proj_perc = tot_hrs / proj_total)

tot_hrs_sx_tbl <- tot_hrs_sx_viz %>%
  mutate(tot_hrs = number(tot_hrs, big.mark = ","),
         proj_total = number(proj_total, big.mark = ","),
         proj_perc = percent(proj_perc, accuracy = 0.01)) %>%
  rename("Project" = project,
         "Gender" = sex,
         "Hours" = tot_hrs, 
         "Project Hours" = proj_total,
         "Project Hours (%)" = proj_perc)                           # Hours by project and gender

tot_hrs_rc_viz <- tot_hours %>%
  group_by(project, race) %>%
  summarize(tot_hrs = sum(total)) %>%
  arrange(project, desc(`tot_hrs`)) %>%
  ungroup() %>%
  left_join(proj_tots, by = "project") %>%
  mutate(proj_perc = tot_hrs / proj_total)

tot_hrs_rc_tbl <- tot_hrs_rc_viz %>%
  mutate(tot_hrs = number(tot_hrs, big.mark = ","),
         proj_total = number(proj_total, big.mark = ","),
         proj_perc = percent(proj_perc, accuracy = 0.01)) %>%
  rename("Project" = project,
         "Race" = race,
         "Hours" = tot_hrs, 
         "Project Hours" = proj_total,
         "Project Hours (%)" = proj_perc)                           # Hours by project and gender

tot_hrs_sxrc_viz <- tot_hours %>%
  group_by(project, sex, race) %>%
  summarize(tot_hrs = sum(total)) %>%
  arrange(project, desc(`tot_hrs`)) %>%
  ungroup() %>%
  left_join(proj_tots, by = "project") %>%
  mutate(proj_perc = tot_hrs / proj_total)

tot_hrs_sxrc_tbl <- tot_hrs_sxrc_viz %>%
  mutate(tot_hrs = number(tot_hrs, big.mark = ","),
         proj_total = number(proj_total, big.mark = ","),
         proj_perc = percent(proj_perc, accuracy = 0.01)) %>%
  rename("Project" = project,
         "Gender" = sex,
         "Race" = race,
         "Hours" = tot_hrs, 
         "Project Hours" = proj_total,
         "Project Hours (%)" = proj_perc)                           # Hours by project and gender/race
```

<br>

### Hours by Gender

<br>

```{r echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE}

tot_hrs_sx_tbl2 <- tot_hrs_sx_tbl %>%
  select(-Project)

kable(tot_hrs_sx_tbl) %>%
  kable_styling(bootstrap_options = c("striped"),
                font_size = 14,
                full_width = TRUE)

```

<br>

### Hours by Race

<br>

```{r echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE}

tot_hrs_rc_tbl2 <- tot_hrs_rc_tbl %>%
  select(-Project)

kable(tot_hrs_rc_tbl2) %>%
  kable_styling(bootstrap_options = c("striped"),
                font_size = 14,
                full_width = TRUE) %>%
  group_rows(group_label = "Hancock International", start_row = 1, end_row = 6) %>%
  group_rows(group_label = "Lakeview Amphitheater", start_row = 7, end_row = 12)

```

<br>


### Gross by Race & Gender

<br>

```{r echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE}

tot_hrs_sxrc_tbl2 <- tot_hrs_sxrc_tbl %>%
  select(-Project)

kable(tot_hrs_sxrc_tbl2) %>%
  kable_styling(bootstrap_options = c("striped"),
                font_size = 14,
                full_width = TRUE) %>%
  group_rows(group_label = "Hancock International", start_row = 1, end_row = 6) %>%
  group_rows(group_label = "Lakeview Amphitheater", start_row = 7, end_row = 17)

```

<br>

## Worker Location

<br>

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}

if(!require(zipcode)){install.packages("zipcode")}
if(!require(noncensus)){install.packages("noncensus")}

library(zipcode)
library(noncensus)

data("zip_codes")
data("counties")

lvhc_loc <- lvhc %>%
  select(project:name, zip, ssn, hours, gross, sex:race) %>%
  filter(!is.na(project),
         !is.na(ssn)) %>%
  mutate(zip = as.character(zip),
         zip = str_pad(zip, width = 5, side = "left", pad = "0")) %>%
  left_join(zip_codes, by = "zip") %>%
  mutate(state_fips = str_extract(fips, "^.{2}"),
         county_fips = str_extract(fips, ".{3}$")) %>%
  left_join(counties, by = c("state", "state_fips", "county_fips")) %>%
  select(project:state, county_name, latitude:fips)

lvhc_loc_tots <- lvhc_loc %>%
  select(project, name, ssn, zip, gross, hours, county_name, state) %>%
  filter(!is.na(project)) %>%
  group_by(project, name, zip, ssn, state, county_name) %>%
  summarize(tot_gross = sum(gross),
            tot_hours = sum(hours)) %>%
  ungroup()
  
county_tots <- lvhc_loc_tots %>%
  group_by(state, county_name) %>%
  summarize(workers = n(),
            tot_gross = sum(tot_gross, na.rm = TRUE),
            tot_hours = sum(tot_hours, na.rm = TRUE)) %>%
  arrange(reorder(county_name, desc(tot_gross))) %>%
  ungroup()

all_tots <- lvhc_loc_tots %>%
  mutate(all_gross = sum(tot_gross, na.rm = TRUE),
         all_hours = sum(tot_hours, na.rm = TRUE)) %>%
  select(county_name, all_gross, all_hours)

all_wrks <- lvhc_loc_tots %>%
  unique() %>%
  group_by(state, county_name) %>%
  summarize(tot_workers = n()) %>%
  select(county_name, tot_workers) %>%
  ungroup() %>%
  mutate(tot_workers = sum(tot_workers, na.rm = TRUE))

county_tots_viz <- county_tots %>%
  left_join(all_tots, by = c("county_name")) %>%
  left_join(all_wrks, by = c("county_name", "state")) %>%
  mutate(gross_perc = tot_gross / all_gross,
         hours_perc = tot_hours / all_hours,
         works_perc = workers / tot_workers) %>%
  unique()

county_tots_tbl <- county_tots_viz %>%
  select(state:workers, works_perc, tot_gross, gross_perc, tot_hours, hours_perc) %>%
  mutate(works_perc = percent(works_perc, accuracy = 0.01),
         hours_perc = percent(hours_perc, accuracy = 0.01),
         gross_perc = percent(gross_perc, accuracy = 0.01),
         tot_gross = dollar(tot_gross, big.mark = ","),
         tot_hours = number(tot_hours, big.mark = ",", accuracy = 0.1)) %>%
  rename("State" = state,
         "County" = county_name,
         "Workers" = workers,
         "Workforce (%)" = works_perc,
         "Hours" = tot_hours,
         "Total Hours (%)" = hours_perc, 
         "Gross" = tot_gross,
         "Total Gross (%)" = gross_perc)                               # Workers, hours, gross by county; LV & HC

proj_loc_tots <- lvhc_loc %>%
  select(project, name, ssn, zip, gross, hours, county_name, state) %>%
  filter(!is.na(project)) %>%
  group_by(project, name, zip, ssn, state, county_name) %>%
  summarize(tot_gross = sum(gross),
            tot_hours = sum(hours)) %>%
  ungroup()

proj_county_tots <- proj_loc_tots %>%
  group_by(project, state, county_name) %>%
  summarize(workers = n(),
            tot_gross = sum(tot_gross, na.rm = TRUE),
            tot_hours = sum(tot_hours, na.rm = TRUE)) %>%
  arrange(project, reorder(county_name, desc(workers))) %>%
  ungroup()

all_tots <- proj_county_tots %>%
  group_by(project) %>%
  summarize(all_gross = sum(tot_gross, na.rm = TRUE),
            all_hours = sum(tot_hours, na.rm = TRUE)) %>%
  select(project, all_gross, all_hours)

all_wrks <- proj_county_tots %>%
  unique() %>%
  group_by(project) %>%
  summarize(tot_workers = sum(workers)) %>%
  ungroup()

proj_county_tots_viz <- proj_county_tots %>%
  left_join(all_tots, by = c("project")) %>%
  left_join(all_wrks, by = "project") %>%
  mutate(gross_perc = tot_gross / all_gross,
         hours_perc = tot_hours / all_hours,
         works_perc = workers / tot_workers) %>%
  unique()

proj_county_tots_tbl <- proj_county_tots_viz %>%
  select(project, state:workers, works_perc, tot_gross, gross_perc, tot_hours, hours_perc) %>%
  mutate(works_perc = percent(works_perc, accuracy = 0.01),
         hours_perc = percent(hours_perc, accuracy = 0.01),
         gross_perc = percent(gross_perc, accuracy = 0.01),
         tot_gross = dollar(tot_gross, big.mark = ","),
         tot_hours = number(tot_hours, big.mark = ",", accuracy = 0.1)) %>%
  rename("Project" = project,
         "State" = state,
         "County" = county_name,
         "Workers" = workers,
         "Project Workforce (%)" = works_perc,
         "Hours" = tot_hours,
         "Project Hours (%)" = hours_perc, 
         "Gross" = tot_gross,
         "Project Gross (%)" = gross_perc)                               # Workers, hours, gross by county; LV & HC

# Workers & Race in Syracuse

if(!require(sf)){install.packages("sf")}
if(!require(tmap)){installe.packages("tmap")}
if(!require(dplyr)){install.packages("dplyr")}
if(!require(readr)){install.packages("readr")}
if(!require(tigris)){install.packages("tigris")}

library(sf)
library(tmap)
library(dplyr)
library(readr)
library(tigris)

```

```{r include=FALSE, results="hide", echo=FALSE, cache=TRUE, warning = FALSE}

options(scipen = 999)

url <- "https://raw.githubusercontent.com/jamisoncrawford/Syracuse-Crime-Analysis/master/Data/fips_geoid.csv"

fips <- read_csv(url)
sf_tracts <- tracts(state = "NY", county = "Onondaga", year = 2016, class = "sf")

sf_tracts <- sf_tracts %>%
  filter(GEOID %in% fips$geoid)

```

```{r include=FALSE, results="hide", echo=FALSE, cache=TRUE, warning = FALSE}

library(tigris)

syr_zips <- zctas(starts_with = "132", year = 2016, state = "NY", class = "sf")

```

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results = "hide"}

map <- tm_shape(syr_zips) +
  tm_fill(col = "skyblue",
          alpha = 1,
          title = "ZIP Codes in Syracuse") +
  tm_borders(alpha = 1,
             col = "white") +
  tm_text(text = "ZCTA5CE10", 
          size = 0.7,
          col = "black") +
  tm_credits(text = "Source:\nU.S. Census Bureau" , 
             align = "left",
             position = c("left", "bottom"),
             size = 0.7) +
  tm_layout(title = "ZIP Codes",
            title.size = 1,
            title.position = c("LEFT", "TOP"), 
            main.title.position = c("LEFT", "TOP"),
            frame = FALSE) +
    tm_shape(sf_tracts) +
    tm_fill(alpha = 0.3,
            col = "tomato") +
    tm_borders(alpha = 0,
               col = "white")                         # Rationale for Inclusion: Map of ZIPs & City Limits


city_zips <- c("13204", "13290", "13208", "13203", "13206", "13202", "13207", "13205", "13210", "13224")

lvhc_loc <- lvhc_loc %>%
  mutate(in_city = NA)

for (i in 1:nrow(lvhc_loc)){
  if (lvhc_loc$zip[i] %in% city_zips){
    lvhc_loc$in_city[i] <- "Within"
  } else {
    lvhc_loc$in_city[i] <- "Outside"
  }
}

lvhc_inds <- lvhc_loc %>%
  group_by(project, name, zip, ssn, sex, race, in_city) %>%
  summarize(tot_weeks = n(),
            tot_hours = sum(hours, na.rm = TRUE),
            tot_gross = sum(gross, na.rm = TRUE)) %>%
  ungroup()
  
city_lims <- lvhc_inds %>%
  group_by(project, race, in_city) %>%
  summarize(tots = n(),
            weeks = sum(tot_weeks),
            hours = sum(tot_hours),
            gross = sum(tot_gross)) %>%
  arrange(project, reorder(in_city, gross)) %>%
  ungroup()

proj_tots <- city_lims %>%
  group_by(project) %>%
  summarize(proj_tots = sum(tots),
            proj_weeks = sum(weeks),
            proj_hours = sum(hours),
            proj_gross = sum(gross))

city_lims_viz <- city_lims %>% 
  left_join(proj_tots, by = "project") %>%
  mutate(wrk_perc = tots / proj_tots,
         wks_perc = weeks / proj_weeks,
         hrs_perc = hours / proj_hours,
         grs_perc = gross / proj_gross)

city_lims_tbl <- city_lims_viz %>%
  select(project:tots, wrk_perc, weeks, wks_perc, hours, hrs_perc, gross, grs_perc) %>%
  mutate(weeks = number(weeks, big.mark = ","),
         hours = number(hours, big.mark = ","),
         gross = dollar(gross, big.mark = ","),
         wrk_perc = percent(wrk_perc, accuracy = 0.01),
         wks_perc = percent(wks_perc, accuracy = 0.01),
         hrs_perc = percent(hrs_perc, accuracy = 0.01),
         grs_perc = percent(grs_perc, accuracy = 0.01)) %>%
  rename("Project" = project,
         "Race" = race,
         "Syracuse" = in_city,
         "Workers" = tots,
         "Proj. Workers (%)" = wrk_perc,
         "Weeks" = weeks,
         "Proj. Weeks (%)" = wks_perc,
         "Hours" = hours,
         "Proj. Hours (%)" = hrs_perc,
         "Gross" = gross,
         "Proj. Gross (%)" = grs_perc)                              # City lims by race

city_lims_overview_viz <- city_lims_viz %>%
  group_by(project, in_city) %>%
  summarize(workers = sum(tots),
            weeks = sum(weeks),
            hours = sum(hours),
            gross = sum(gross)) %>%
  ungroup() %>%
  left_join(proj_tots, by = "project") %>%
  mutate(wrk_perc = workers / proj_tots,
         wks_perc = weeks / proj_weeks,
         hrs_perc = hours / proj_hours,
         grs_perc = gross / proj_gross)

city_lims_overview_tbl <- city_lims_overview_viz %>%
  select(project:workers, wrk_perc, weeks, wks_perc, hours, hrs_perc, gross, grs_perc) %>%
  mutate(weeks = number(weeks, big.mark = ","),
         hours = number(hours, big.mark = ","),
         gross = dollar(gross, big.mark = ","),
         wrk_perc = percent(wrk_perc, accuracy = 0.01),
         wks_perc = percent(wks_perc, accuracy = 0.01),
         hrs_perc = percent(hrs_perc, accuracy = 0.01),
         grs_perc = percent(grs_perc, accuracy = 0.01)) %>%
  rename("Project" = project,
         "Syracuse" = in_city,
         "Workers" = workers,
         "Proj. Workers (%)" = wrk_perc,
         "Weeks" = weeks,
         "Proj. Weeks (%)" = wks_perc,
         "Hours" = hours,
         "Proj. Hours (%)" = hrs_perc,
         "Gross" = gross,
         "Proj. Gross (%)" = grs_perc)

```

<br>

### Location by County

<br>

```{r echo = FALSE, message = FALSE, warning = FALSE}

library(kableExtra)

kable(county_tots_tbl) %>%
  kable_styling(bootstrap_options = c("striped"),
                font_size = 14,
                full_width = TRUE)

```

<br>

### Location by Project, County

<br>

```{r echo = FALSE, message = FALSE, warning = FALSE}

library(dplyr)

proj_county_tots_tbl2 <- proj_county_tots_tbl %>%
  select(-Project)

kable(proj_county_tots_tbl2) %>%
  kable_styling(bootstrap_options = c("striped"),
                font_size = 14,
                full_width = TRUE) %>%
  group_rows(group_label = "Hancock International", start_row = 1, end_row = 26) %>%
  group_rows(group_label = "Lakeview Amphitheater", start_row = 27, end_row = 55)

```

<br>

### Defining City Limits

<br>

**Note****:** ZIP codes within Syracuse city limits are defined as ZIP code areas in which more than 50% of its areas falls within Syracuse city limits, defined as 55 census tracts per U.S. Census Bureau. Therefore, the following ZIP codes are considered within city limits:

* 13204
* 13290
* 13208
* 13203
* 13206
* 13202
* 13207
* 13205
* 13210
* 13224

<br>

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width=12, fig.height=7, cache=TRUE}
map
```

<br>

### Workers in Syracuse

<br>

```{r echo = FALSE, message = FALSE, warning = FALSE}

kable(city_lims_overview_tbl) %>%
  kable_styling(bootstrap_options = c("striped"),
                font_size = 14,
                full_width = TRUE)
```

<br>

### Workers in Syracuse by Race

<br>

```{r echo = FALSE, message = FALSE, warning = FALSE}

city_lims_tbl2 <- city_lims_tbl %>%
  select(-Project)

kable(city_lims_tbl2) %>%
  kable_styling(bootstrap_options = c("striped"),
                font_size = 14,
                full_width = TRUE)%>%
  group_rows(group_label = "Hancock International", start_row = 1, end_row = 11) %>%
  group_rows(group_label = "Lakeview Amphitheater", start_row = 12, end_row = 20)

```

<br>
